Phenomenological Robotics

### 2011-12-22 draft.tex
Finished writing about affordances in robotics.

>>>>

Moratz and Tenbrink~\cite{moratz2008} discuss advances in \emph{spatial
cognition} and develop a method that allows a robot to acquire knowledge through
its interaction with a human. They also present an object recognition system
based in \emph{affordances}, but do not provide detailed on the matter.

Paletta and Fritz~\cite{paletta2008} describe a process of \emph{affordance
cueing} where a robot obtains a probability distribution over the possible
affordances from a set of features. They apply it to a scenario where a robot
interacts with magnetizable cans that might afford ``lifting'', using
Reinforcement Learning and Markov Decision Process to learn which features
might indicate the ``liftability'' of an object.
